---
title: "NEET and mental health meta-analyses"
author: "Sofia Danna"
date: 8 June 2020
output:
  html_document:
    df_print: paged
---

# Mise en place

* Code
    + The completed code in this document was written using dplyr; the analyses that are "commented out" have yet to be translated. In order to check the results of translated code against previous correct results, use Results - metaanalysis 20200507.html.

* Analysis: 
    + The following tutorial was used for analyses: <https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/> 
    + Main analyses are random effects models; subgroup analyses are fixed effects models.

* Data
    + The neet dataframe was updated several times as analyses developed. As of May 25, 2020, all analyses can run using this unified dataset. The Repeated_measures column was created by Gen to avoid repeated (overlapping) samples being pooled together in main analyses. However, different estimates may overlap in other ways in different analyses, so columns beginning with rep_ were added to the end of the dataset to help eliminate estimates that need to be removed for each analysis (i.e., rep_dis.gender for the gender subgroup analysis of distress estimates).

```{r}
# On Sofia's Douglas Windows computer
#neet <- read.csv("C:/Users/dansof/Dropbox/PEPP new/NEET meta-analysis/metaanalysis/neet 20200525.csv")

# On Sofia's personal Mac
neet <- read.csv("~/Dropbox/PEPP/NEET meta-analysis/metaanalysis/neet 20200608.csv")
```

checking out the variables in the dataframe
```{r}
neet
str(neet)
```

installing and loading meta package
```{r message=FALSE, warning=FALSE}
install.packages("meta", repos = "http://cran.us.r-project.org")
install.packages("dplyr", repos = "http://cran.us.r-project.org")
library(meta)
library(metafor)
library(dplyr)
```

Parameter       | Function
----------------|---------------------------------------------------------------------------------
TE	            | This tells R to use the TE column to retrieve the effect sizes for each study
seTE	          | This tells R to use the seTE column to retrieve the standard error for each study
data=	          | After =, paste the name of your dataset here
studlab=paste()	| This tells the function were the labels for each study are stored. If you named the spreadsheet columns as advised, this should be studlab=paste(Author)
comb.fixed=	    | Whether to use a fixed-effects-model
comb.random=	  | Whether to use a random-effects-model. This has to be set to TRUE
method.tau=	    | Which estimator to use for the between-study variance
hakn=	          | Whether to use the Knapp-Hartung method
prediction=	    | Whether to print a prediction interval for the effect of future studies based on present evidence
sm=	            | The summary measure we want to calculate. We can either calculate the mean difference (MD) or Hedges’ g (SMD)

Using the instructions from the tutorial by Mathias Harrer (url above),

instead of | we will use
-----------|-----------
"Author"   | "Study"
"TE"       | "OR_ln"
"seTE"     | "SE"

# Analyses: Mental health measure

## DISTRESS

```{r}
dis <- filter(neet, Distress==1 & is.na(Repeated_sample)==TRUE & is.na(rep_dis)==TRUE & !is.na(OR_ln))

dis

meta.dis <- metagen(OR_ln,
                    SE,
                    data=dis,
                    studlab=paste(Study),
                    comb.fixed = FALSE,
                    comb.random = TRUE,
                    method.tau = "DL",
                    hakn = FALSE,
                    prediction=FALSE,
                    sm="OR")

meta.dis

forest(meta.dis)
```

### DISTRESS - directionality

```{r}
dis.dir <- filter(neet, Distress==1 & Gender=="all")

dis.dir

meta.dis.dir <- metagen(OR_ln,
                        SE,
                        data=dis.dir,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.dis.dir<-update.meta(meta.dis.dir,
                          byvar=Temporality.of.measures, 
                          comb.random = F, 
                          comb.fixed = T)

meta.dis.dir

forest(meta.dis.dir)
```

### DISTRESS - age

```{r}
dis.age <- filter(neet, Distress==1 & Gender=="all" & is.na(Age_at_interview)==FALSE)

dis.age

meta.dis.age <- metagen(OR_ln,
                        SE,
                        data=dis.age,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.dis.age<-update.meta(meta.dis.age, 
                          byvar=Age_at_interview, 
                          comb.random = F, 
                          comb.fixed = T)

meta.dis.age

forest(meta.dis.age)
```

### DISTRESS - gender

```{r}
dis.gen <- filter(neet, Distress==1 & Gender!="all" & is.na(Repeated_sample))

dis.gen

meta.dis.gen <- metagen(OR_ln,
                        SE,
                        data=dis.gen,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.dis.gen<-update.meta(meta.dis.gen,
                          byvar=Gender, 
                          comb.random = F, 
                          comb.fixed = T)

meta.dis.gen

forest(meta.dis.gen)
```

***

## MOOD 

```{r}
mood <- filter(neet, Mood==1 & Gender=="all" & is.na(Repeated_sample) & !is.na(OR_ln))

mood

meta.mood <- metagen(OR_ln,
                     SE,
                     data=mood,
                     studlab=paste(Study),
                     comb.fixed = FALSE,
                     comb.random = TRUE,
                     method.tau = "DL",
                     hakn = FALSE,
                     prediction=FALSE,
                     sm="OR")

meta.mood

forest(meta.mood)
```

### MOOD - directionality

```{r}
mood.dir <- filter(neet, Mood==1 & Gender=="all")
 
mood.dir

meta.mood.dir <- metagen(OR_ln,
                         SE,
                         data=mood.dir,
                         studlab=paste(Study),
                         comb.fixed = FALSE,
                         comb.random = TRUE,
                         method.tau = "DL",
                         hakn = FALSE,
                         prediction=FALSE,
                         sm="OR")

meta.mood.dir<-update.meta(meta.mood.dir,
                           byvar=Temporality.of.measures, 
                           comb.random = F, 
                           comb.fixed = T)

meta.mood.dir
 
forest(meta.mood.dir)
```

### MOOD - age

```{r}
mood.age <- filter(neet, Mood==1 & Gender=="all" & is.na(rep_mood.age) & is.na(Age_at_interview)==FALSE)

mood.age

meta.mood.age <- metagen(OR_ln,
                         SE,
                         data=mood.age,
                         studlab=paste(Study),
                         comb.fixed = FALSE,
                         comb.random = TRUE,
                         method.tau = "DL",
                         hakn = FALSE,
                         prediction=FALSE,
                         sm="OR")

meta.mood.age<-update.meta(meta.mood.age,
                           byvar=Age_at_interview, 
                           comb.random = F, 
                           comb.fixed = T)

meta.mood.age

forest(meta.mood.age)
```

### MOOD - gender

```{r}
mood.gen <- filter(neet, Mood==1 & Gender!="all")

mood.gen
```

***

## ANXIETY 

```{r}
anx <- filter(neet, Anxiety==1 & Gender=="all" & is.na(Repeated_sample) & !is.na(OR_ln))

anx

meta.anx <- metagen(OR_ln,
                    SE,
                    data=anx,
                    studlab=paste(Study),
                    comb.fixed = FALSE,
                    comb.random = TRUE,
                    method.tau = "DL",
                    hakn = FALSE,
                    prediction=FALSE,
                    sm="OR")

meta.anx

forest(meta.anx)
```

### ANXIETY - directionality

```{r}
anx.dir <- filter(neet, Anxiety==1 & Gender=="all")

anx.dir

meta.anx.dir <- metagen(OR_ln,
                        SE,
                        data=anx.dir,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.anx.dir<-update.meta(meta.anx.dir,
                          byvar=Temporality.of.measures, 
                          comb.random = F, 
                          comb.fixed = T)

meta.anx.dir

forest(meta.anx.dir)
```

### ANXIETY - age

```{r}
anx.age <- filter(neet, Anxiety==1 & Gender=="all" & is.na(rep_anx.age) & is.na(Age_at_interview)==FALSE)

anx.age

meta.anx.age <- metagen(OR_ln,
                        SE,
                        data=anx.age,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.anx.age<-update.meta(meta.anx.age, 
                          byvar=Age_at_interview, 
                          comb.random = F, 
                          comb.fixed = T)

meta.anx.age

forest(meta.anx.age)
```

### ANXIETY - gender

```{r}
anx.gen <- filter(neet, Anxiety==1 & Gender!="all" & is.na(Repeated_sample))

anx.gen

meta.anx.gen <- metagen(OR_ln,
                        SE,
                        data=anx.gen,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.anx.gen<-update.meta(meta.anx.gen, 
                          byvar=Gender, 
                          comb.random = F, 
                          comb.fixed = T)

meta.anx.gen

forest(meta.anx.gen)
```

***

## BEHAVIOURAL

```{r}
beh <- filter(neet, Behavioral==1 & Gender=="all" & is.na(Repeated_sample) & is.na(rep_beh))

beh

meta.beh <- metagen(OR_ln,
                    SE,
                    data=beh,
                    studlab=paste(Study),
                    comb.fixed = FALSE,
                    comb.random = TRUE,
                    method.tau = "DL",
                    hakn = FALSE,
                    prediction=FALSE,
                    sm="OR")

meta.beh

forest(meta.beh)
```

### BEHAVIOURAL - directionality

```{r}
beh.dir <- filter(neet, Behavioral==1 & Gender=="all")
 
beh.dir
 
meta.beh.dir <- metagen(OR_ln,
                        SE,
                        data=beh.dir,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.beh.dir<-update.meta(meta.beh.dir,
                          byvar=Temporality.of.measures, 
                          comb.random = F, 
                          comb.fixed = T)

meta.beh.dir
 
forest(meta.beh.dir)
```

### BEHAVIOURAL - age

```{r}
beh.age <- filter(neet, Behavioral==1 & Gender=="all" & is.na(rep_beh.age) & is.na(Age_at_interview)==FALSE)

beh.age

meta.beh.age <- metagen(OR_ln,
                        SE,
                        data=beh.age,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.beh.age<-update.meta(meta.beh.age,
                          byvar=Age_at_interview, 
                          comb.random = F, 
                          comb.fixed = T)

meta.beh.age

forest(meta.beh.age)
```

### BEHAVIOURAL - gender

```{r}
beh.gen <- filter(neet, Behavioral==1 & Gender!="all" & is.na(Repeated_sample))

beh.gen

meta.beh.gen <- metagen(OR_ln,
                        SE,
                        data=beh.gen,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.beh.gen<-update.meta(meta.beh.gen,
                          byvar=Gender, 
                          comb.random = F, 
                          comb.fixed = T)

meta.beh.gen

forest(meta.beh.gen)
```

***

## ALCOHOL

```{r}
alc <- filter(neet, Alcohol==1 & Gender=="all" & is.na(Repeated_sample) & !is.na(OR_ln))

alc

meta.alc <- metagen(OR_ln,
                    SE,
                    data=alc,
                    studlab=paste(Study),
                    comb.fixed = FALSE,
                    comb.random = TRUE,
                    method.tau = "DL",
                    hakn = FALSE,
                    prediction=FALSE,
                    sm="OR")

meta.alc

forest(meta.alc)
```

### ALCOHOL - directionality

```{r}
alc.dir <- filter(neet, Alcohol==1 & Gender=="all")

alc.dir

meta.alc.dir <- metagen(OR_ln,
                        SE,
                        data=alc.dir,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.alc.dir<-update.meta(meta.alc.dir,
                          byvar=Temporality.of.measures, 
                          comb.random = F, 
                          comb.fixed = T)

meta.alc.dir

forest(meta.alc.dir)
```

### ALCOHOL - age

```{r}
alc.age <- filter(neet, Alcohol==1 & Gender=="all" & is.na(rep_alc.age) & is.na(Age_at_interview)==FALSE)

alc.age

meta.alc.age <- metagen(OR_ln,
                     SE,
                     data=alc.age,
                     studlab=paste(Study),
                     comb.fixed = FALSE,
                     comb.random = TRUE,
                     method.tau = "DL",
                     hakn = FALSE,
                     prediction=FALSE,
                     sm="OR")

meta.alc.age<-update.meta(meta.alc.age,
                          byvar=Age_at_interview, 
                          comb.random = F, 
                          comb.fixed = T)

meta.alc.age

forest(meta.alc.age)
```

### ALCOHOL - gender

```{r}
alc.gen <- filter(neet, Alcohol==1 & Gender!="all")

alc.gen
```

***

## CANNABIS

```{r}
can <- filter(neet, Cannabis==1 & Gender=="all" & is.na(Repeated_sample))

can

meta.can <- metagen(OR_ln,
                    SE,
                    data=can,
                    studlab=paste(Study),
                    comb.fixed = FALSE,
                    comb.random = TRUE,
                    method.tau = "DL",
                    hakn = FALSE,
                    prediction=FALSE,
                    sm="OR")

meta.can

forest(meta.can)
```

### CANNABIS - directionality

```{r}
meta.can.dir<-update.meta(meta.can,
                          byvar=Temporality.of.measures, 
                          comb.random = F, 
                          comb.fixed = T)

meta.can.dir

forest(meta.can.dir)
```

### CANNABIS - age

```{r}
can.age <- filter(neet, Cannabis==1 & Gender=="all" & is.na(Age_at_interview)==FALSE)

can.age

meta.can.age <- metagen(OR_ln,
                     SE,
                     data=can.age,
                     studlab=paste(Study),
                     comb.fixed = FALSE,
                     comb.random = TRUE,
                     method.tau = "DL",
                     hakn = FALSE,
                     prediction=FALSE,
                     sm="OR")

meta.can.age<-update.meta(meta.can.age, 
                          byvar=Age_at_interview, 
                          comb.random = F, 
                          comb.fixed = T)

meta.can.age

forest(meta.can.age)
```

### CANNABIS - gender

```{r}
can.gen <- filter(neet, Cannabis==1 & Gender!="all")

can.gen
```

***

## DRUG 

```{r}
drg <- filter(neet, Drug==1 & Gender=="all" & is.na(Repeated_sample) & is.na(rep_drg) & !is.na(OR_ln))

drg

meta.drg <- metagen(OR_ln,
                    SE,
                    data=drg,
                    studlab=paste(Study),
                    comb.fixed = FALSE,
                    comb.random = TRUE,
                    method.tau = "DL",
                    hakn = FALSE,
                    prediction=FALSE,
                    sm="OR")

meta.drg

forest(meta.drg)
```

### DRUG - directionality

```{r}
drg.dir <- filter(neet, Drug==1 & Gender=="all")

drg.dir

meta.drg.dir <- metagen(OR_ln,
                        SE,
                        data=drg.dir,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.drg.dir<-update.meta(meta.drg.dir,
                          byvar=Temporality.of.measures, 
                          comb.random = F, 
                          comb.fixed = T)

meta.drg.dir

forest(meta.drg.dir)
```

### DRUG - age

```{r}
drg.age <- filter(neet, Drug==1 & Gender=="all" & is.na(rep_drg.age) & is.na(Age_at_interview)==FALSE)

drg.age

meta.drg.age <- metagen(OR_ln,
                        SE,
                        data=drg.age,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.drg.age<-update.meta(meta.drg.age,
                          byvar=Age_at_interview, 
                          comb.random = F, 
                          comb.fixed = T)

meta.drg.age

forest(meta.drg.age)
```

### DRUG - gender

```{r}
drg.gen <- filter(neet, Drug==1 & Gender!="all" & is.na(Repeated_sample))

drg.gen

meta.drg.gen <- metagen(OR_ln,
                        SE,
                        data=drg.gen,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.drg.gen<-update.meta(meta.drg.gen, 
                          byvar=Gender, 
                          comb.random = F, 
                          comb.fixed = T)

meta.drg.gen

forest(meta.drg.gen)
```

***

## SUICIDAL

```{r}
sui <- filter(neet, Suicidal==1 & Gender=="all" & is.na(Repeated_sample))

sui

meta.sui <- metagen(OR_ln,
                    SE,
                    data=sui,
                    studlab=paste(Study),
                    comb.fixed = FALSE,
                    comb.random = TRUE,
                    method.tau = "DL",
                    hakn = FALSE,
                    prediction=FALSE,
                    sm="OR")

meta.sui

forest(meta.sui)
```

### SUICIDAL - directionality

```{r}
sui.dir <- filter(neet, Suicidal==1 & Gender=="all")

sui.dir

meta.sui.dir <- metagen(OR_ln,
                        SE,
                        data=sui.dir,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.sui.dir<-update.meta(meta.sui.dir, 
                          byvar=Temporality.of.measures, 
                          comb.random = F, 
                          comb.fixed = T)

meta.sui.dir

forest(meta.sui.dir)
```

### SUICIDAL - age

```{r}
sui.age <- filter(neet, Suicidal==1 & Gender=="all" & is.na(rep_sui.age) & is.na(Age_at_interview)==FALSE)

sui.age

meta.sui.age <- metagen(OR_ln,
                        SE,
                        data=sui.age,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.sui.age<-update.meta(meta.sui.age, 
                          byvar=Age_at_interview, 
                          comb.random = F, 
                          comb.fixed = T)

meta.sui.age

forest(meta.sui.age)
```

Pooling *suicidal attempts* in youth aged 18 and over, i.e., Power 2015 (OR 3.1) and Gutierrez 2018 (OR 2.75)

```{r}
suiatt <- filter(neet, Mental.health.measures %in% c("Suicidal attempt", "Suicidal attempts (lifetime)") & 
              Gender=="all" & Age_at_interview==">=18" & is.na(rep_sui.age))

suiatt
                          
meta.suiatt <- metagen(OR_ln,
                     SE,
                     data=suiatt,
                     studlab=paste(Study),
                     comb.fixed = T,
                     comb.random = F,
                     method.tau = "DL",
                     hakn = FALSE,
                     prediction=FALSE,
                     sm="OR")

meta.suiatt

forest(meta.suiatt)
```

### SUICIDAL - gender

```{r}
sui.gen <- filter(neet, Suicidal==1 & Gender!="all")

sui.gen
```

***

## ANY

Gen says to use Power 2015's "Any lifetime disorder" for main analysis
```{r}
any <- filter(neet, Any==1 & Gender=="all" & is.na(rep_any))

any

meta.any <- metagen(OR_ln,
                    SE,
                    data=any,
                    studlab=paste(Study),
                    comb.fixed = FALSE,
                    comb.random = TRUE,
                    method.tau = "DL",
                    hakn = FALSE,
                    prediction=FALSE,
                    sm="OR")

meta.any

forest(meta.any)
```

### ANY - directionality

Gen says to use Power 2015's "Any diagnosis in adol" for directionality subgroup analysis
```{r}
any.dir <- filter(neet, Any==1 & Gender=="all" & is.na(rep_any.dir))

any.dir

meta.any.dir <- metagen(OR_ln,
                        SE,
                        data=any.dir,
                        studlab=paste(Study),
                        comb.fixed = FALSE,
                        comb.random = TRUE,
                        method.tau = "DL",
                        hakn = FALSE,
                        prediction=FALSE,
                        sm="OR")

meta.any.dir<-update.meta(meta.any.dir, 
                          byvar=Temporality.of.measures, 
                          comb.random = F, 
                          comb.fixed = T)

meta.any.dir

forest(meta.any.dir)
```

### ANY - age

using "Any lifetime disorder" because it's the more comprehensive measure
```{r}
any.age  <- filter(neet, Any==1 & Gender=="all" & is.na(rep_any))

any.age

meta.any.age <- metagen(OR_ln,
                     SE,
                     data=any.age,
                     studlab=paste(Study),
                     comb.fixed = FALSE,
                     comb.random = TRUE,
                     method.tau = "DL",
                     hakn = FALSE,
                     prediction=FALSE,
                     sm="OR")

meta.any.age<-update.meta(meta.any.age, 
                          byvar=Age_at_interview, 
                          comb.random = F, 
                          comb.fixed = T)

meta.any.age

forest(meta.any.age)
```

### ANY - gender

```{r}
any.gen <- filter(neet, Any==1 & Gender!="all")

any.gen
```
