---
title: "NEET and mental health meta-analyses"
author: "Sofia Danna"
date: "14 November 2019"
output:
  html_document:
    df_print: paged
---


# Mise en place

Will be using this tutorial for analyses: <https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/> 


These are the updated data that Gen and I decided on 18 October 2019.
There should no longer be any repeated samples pooled together. 
All variables should be accurately re-derived. It was the dataset Sofia saved after running all of these analyses in R. 

```{r}
neet2 <- read.csv("C:/Users/dansof/Dropbox/PEPP new/NEET meta-analysis/metaanalysis/neet2.csv")
```

checking out the variables in the updated NEET dataframe
```{r}
neet2
str(neet2)
```


installing and loading meta package
```{r}
install.packages("meta", repos = "http://cran.us.r-project.org")
library(meta)
library(metafor)
```

Parameter       | Function
----------------|---------------------------------------------------------------------------------
TE	            | This tells R to use the TE column to retrieve the effect sizes for each study
seTE	          | This tells R to use the seTE column to retrieve the standard error for each study
data=	          | After =, paste the name of your dataset here
studlab=paste()	|  This tells the function were the labels for each study are stored. If you named the spreadsheet columns as advised, this should be studlab=paste(Author)
comb.fixed=	    | Whether to use a fixed-effects-model
comb.random=	  | Whether to use a random-effects-model. This has to be set to TRUE
method.tau=	    | Which estimator to use for the between-study variance
hakn=	          |   Whether to use the Knapp-Hartung method
prediction=	    | Whether to print a prediction interval for the effect of future studies based on present evidence
sm=	            | The summary measure we want to calculate. We can either calculate the mean difference (MD) or Hedges’ g (SMD)


using the instructions from the tutorial by Mathias Harrer (url above),

instead of | we will use
-----------|-----------
"Author"   | "Study"
"TE"       | "OR_ln"
"seTE"     | "SE"


# Analyses: Mental health measure


## DISTRESS
distress = 1, gender = all, repeated sample = 0

```{r}
MHdis.Gall.rep0 <- neet2[which(neet2$Distress==1 & neet2$Gender=="all" & is.na(neet2$Repeated_sample)),]

head(MHdis.Gall.rep0)


meta.MHdis.Gall.rep0 <- metagen(OR_ln,
                     SE,
                     data=MHdis.Gall.rep0,
                     studlab=paste(Study),
                     comb.fixed = FALSE,
                     comb.random = TRUE,
                     method.tau = "DL",
                     hakn = FALSE,
                     prediction=FALSE,
                     sm="OR")
meta.MHdis.Gall.rep0

forest(meta.MHdis.Gall.rep0)
```


### DISTRESS - directionality

```{r}

MHdis.Gall.rep1 <- neet2[which(neet2$Distress==1 & neet2$Gender=="all"),]

head(MHdis.Gall.rep1)


meta.MHdis.Gall.rep1 <- metagen(OR_ln,
                     SE,
                     data=MHdis.Gall.rep1,
                     studlab=paste(Study),
                     comb.fixed = FALSE,
                     comb.random = TRUE,
                     method.tau = "DL",
                     hakn = FALSE,
                     prediction=FALSE,
                     sm="OR")
meta.MHdis.Gall.rep1

meta.MHdis.Gall.rep1.dir<-update.meta(meta.MHdis.Gall.rep0, 
                                 byvar=Temporality.of.measures, 
                                 comb.random = TRUE, 
                                 comb.fixed = FALSE)
meta.MHdis.Gall.rep1.dir


forest(meta.MHdis.Gall.rep1.dir)
```


### DISTRESS - geography

```{r}
meta.MHdis.Gall.rep0.geo<-update.meta(meta.MHdis.Gall.rep0, 
                                      byvar=Country, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHdis.Gall.rep0.geo

forest(meta.MHdis.Gall.rep0.geo)
```


### DISTRESS - gender

```{r}
MHdis.Gbg.rep0 <- neet2[which(neet2$Distress==1 & neet2$Gender!="all" & is.na(neet2$Repeated_sample)),]

head(MHdis.Gbg.rep0)


meta.MHdis.Gbg.rep0 <- metagen(OR_ln,
                                SE,
                                data=MHdis.Gbg.rep0,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHdis.Gbg.rep0


meta.MHdis.Gbg.rep0<-update.meta(meta.MHdis.Gbg.rep0, 
                                      byvar=Gender, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHdis.Gbg.rep0

forest(meta.MHdis.Gbg.rep0)
```


## MOOD 
mood = 1, gender = all, repeated sample = 0

```{r}
MHmood.Gall.rep0 <- neet2[which(neet2$Mood==1 & neet2$Gender=="all" & is.na(neet2$Repeated_sample)),]

head(MHmood.Gall.rep0)


meta.MHmood.Gall.rep0 <- metagen(OR_ln,
                                SE,
                                data=MHmood.Gall.rep0,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHmood.Gall.rep0
```



### MOOD - directionality

```{r}
MHmood.Gall.rep1 <- neet2[which(neet2$Mood==1 & neet2$Gender=="all"),]

head(MHmood.Gall.rep1)


meta.MHmood.Gall.rep1 <- metagen(OR_ln,
                                SE,
                                data=MHmood.Gall.rep1,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHmood.Gall.rep1

meta.MHmood.Gall.rep1.dir<-update.meta(meta.MHmood.Gall.rep1, 
                                      byvar=Temporality.of.measures, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHmood.Gall.rep1.dir

forest(meta.MHmood.Gall.rep1.dir)
```


### MOOD - geography

```{r}
meta.MHmood.Gall.rep0.geo<-update.meta(meta.MHmood.Gall.rep0, 
                                      byvar=Country, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHmood.Gall.rep0.geo

forest(meta.MHmood.Gall.rep0.geo)
```


### MOOD - gender

```{r}
MHmood.Gbg.rep0 <- neet2[which(neet2$Mood==1 & neet2$Gender!="all" & is.na(neet2$Repeated_sample)),]

head(MHmood.Gbg.rep0)
```


## ANXIETY 

anxiety = 1, gender = all, repeated sample = 0

```{r}
MHanx.Gall.rep0 <- neet2[which(neet2$Anxiety==1 & neet2$Gender=="all" & is.na(neet2$Repeated_sample)),]

head(MHanx.Gall.rep0)

meta.MHanx.Gall.rep0 <- metagen(OR_ln,
                                 SE,
                                 data=MHanx.Gall.rep0,
                                 studlab=paste(Study),
                                 comb.fixed = FALSE,
                                 comb.random = TRUE,
                                 method.tau = "DL",
                                 hakn = FALSE,
                                 prediction=FALSE,
                                 sm="OR")
meta.MHanx.Gall.rep0
```


### ANXIETY - directionality

```{r}
MHanx.Gall.rep1 <- neet2[which(neet2$Anxiety==1 & neet2$Gender=="all"),]

head(MHanx.Gall.rep1)

meta.MHanx.Gall.rep1 <- metagen(OR_ln,
                                 SE,
                                 data=MHanx.Gall.rep1,
                                 studlab=paste(Study),
                                 comb.fixed = FALSE,
                                 comb.random = TRUE,
                                 method.tau = "DL",
                                 hakn = FALSE,
                                 prediction=FALSE,
                                 sm="OR")
meta.MHanx.Gall.rep1
meta.MHanx.Gall.rep1.dir<-update.meta(meta.MHanx.Gall.rep1, 
                                       byvar=Temporality.of.measures, 
                                       comb.random = TRUE, 
                                       comb.fixed = FALSE)
meta.MHanx.Gall.rep1.dir

forest(meta.MHanx.Gall.rep1.dir)
```


### ANXIETY - geography

```{r}
meta.MHanx.Gall.rep0.geo<-update.meta(meta.MHanx.Gall.rep0, 
                                       byvar=Country, 
                                       comb.random = TRUE, 
                                       comb.fixed = FALSE)
meta.MHanx.Gall.rep0.geo

forest(meta.MHanx.Gall.rep0.geo)
```


### ANXIETY - gender

```{r}
MHanx.Gbg.rep0 <- neet2[which(neet2$Anxiety==1 & neet2$Gender!="all" & is.na(neet2$Repeated_sample)),]

head(MHanx.Gbg.rep0)

meta.MHanx.Gbg.rep0 <- metagen(OR_ln,
                               SE,
                               data=MHanx.Gbg.rep0,
                               studlab=paste(Study),
                               comb.fixed = FALSE,
                               comb.random = TRUE,
                               method.tau = "DL",
                               hakn = FALSE,
                               prediction=FALSE,
                               sm="OR")
meta.MHanx.Gbg.rep0


meta.MHanx.Gbg.rep0<-update.meta(meta.MHanx.Gbg.rep0, 
                                 byvar=Gender, 
                                 comb.random = TRUE, 
                                 comb.fixed = FALSE)
meta.MHanx.Gbg.rep0

forest(meta.MHanx.Gbg.rep0)
```


## BEHAVIOURAL

behavioural = 1, gender = all, repeated sample = 0

```{r}
MHbeh.Gall.rep0 <- neet2[which(neet2$Behavioral==1 & neet2$Gender=="all" & is.na(neet2$Repeated_sample)),]

head(MHbeh.Gall.rep0)

meta.MHbeh.Gall.rep0 <- metagen(OR_ln,
                                SE,
                                data=MHbeh.Gall.rep0,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHbeh.Gall.rep0
```

### BEHAVIOURAL - directionality

```{r}
MHbeh.Gall.rep1 <- neet2[which(neet2$Behavioral==1 & neet2$Gender=="all"),]

head(MHbeh.Gall.rep1)

meta.MHbeh.Gall.rep1 <- metagen(OR_ln,
                                SE,
                                data=MHbeh.Gall.rep1,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHbeh.Gall.rep1

meta.MHbeh.Gall.rep1.dir<-update.meta(meta.MHbeh.Gall.rep1, 
                                      byvar=Temporality.of.measures, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHbeh.Gall.rep1.dir

forest(meta.MHbeh.Gall.rep1.dir)
```


### BEHAVIOURAL - geography

```{r}
meta.MHbeh.Gall.rep0.geo<-update.meta(meta.MHbeh.Gall.rep0, 
                                      byvar=Country, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHbeh.Gall.rep0.geo

forest(meta.MHbeh.Gall.rep0.geo)
```


### BEHAVIOURAL - gender

```{r}
MHbeh.Gbg.rep0 <- neet2[which(neet2$Behavioral==1 & neet2$Gender!="all" & is.na(neet2$Repeated_sample)),]

head(MHbeh.Gbg.rep0)

meta.MHbeh.Gbg.rep0 <- metagen(OR_ln,
                               SE,
                               data=MHbeh.Gbg.rep0,
                               studlab=paste(Study),
                               comb.fixed = FALSE,
                               comb.random = TRUE,
                               method.tau = "DL",
                               hakn = FALSE,
                               prediction=FALSE,
                               sm="OR")
meta.MHbeh.Gbg.rep0


meta.MHbeh.Gbg.rep0<-update.meta(meta.MHbeh.Gbg.rep0, 
                                 byvar=Gender, 
                                 comb.random = TRUE, 
                                 comb.fixed = FALSE)
meta.MHbeh.Gbg.rep0

forest(meta.MHbeh.Gbg.rep0)
```


## ALCOHOL
alcohol = 1, gender = all, repeated sample = 0

```{r}
MHalc.Gall.rep0 <- neet2[which(neet2$Alcohol==1 & neet2$Gender=="all" & is.na(neet2$Repeated_sample)),]

head(MHalc.Gall.rep0)

meta.MHalc.Gall.rep0 <- metagen(OR_ln,
                                SE,
                                data=MHalc.Gall.rep0,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHalc.Gall.rep0
```


### ALCOHOL - directionality

```{r}

MHalc.Gall.rep1 <- neet2[which(neet2$Alcohol==1 & neet2$Gender=="all"),]

head(MHalc.Gall.rep1)

meta.MHalc.Gall.rep1 <- metagen(OR_ln,
                                SE,
                                data=MHalc.Gall.rep1,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHalc.Gall.rep1

meta.MHalc.Gall.rep1.dir<-update.meta(meta.MHalc.Gall.rep1, 
                                      byvar=Temporality.of.measures, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHalc.Gall.rep1.dir

forest(meta.MHalc.Gall.rep1.dir)
```


### ALCOHOL - geography 

```{r}
meta.MHalc.Gall.rep0.geo<-update.meta(meta.MHalc.Gall.rep0, 
                                      byvar=Country, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHalc.Gall.rep0.geo

forest(meta.MHalc.Gall.rep0.geo)
```


### ALCOHOL - gender

```{r}
MHalc.Gbg.rep0 <- neet2[which(neet2$Alcohol==1 & neet2$Gender!="all" & is.na(neet2$Repeated_sample)),]

head(MHalc.Gbg.rep0)
```


## CANNABIS

cannabis = 1, gender = all, repeated sample = 0

```{r}
MHcan.Gall.rep0 <- neet2[which(neet2$Cannabis==1 & neet2$Gender=="all" & is.na(neet2$Repeated_sample)),]

head(MHcan.Gall.rep0)

meta.MHcan.Gall.rep0 <- metagen(OR_ln,
                                SE,
                                data=MHcan.Gall.rep0,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHcan.Gall.rep0
```


### CANNABIS - directionality

```{r}
meta.MHcan.Gall.rep0.dir<-update.meta(meta.MHcan.Gall.rep0, 
                                      byvar=Temporality.of.measures, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHcan.Gall.rep0.dir

forest(meta.MHcan.Gall.rep0.dir)
```


### CANNABIS - geography

```{r}
meta.MHcan.Gall.rep0.geo<-update.meta(meta.MHcan.Gall.rep0, 
                                      byvar=Country, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHcan.Gall.rep0.geo

forest(meta.MHcan.Gall.rep0.geo)
```


### CANNABIS - gender

```{r}
MHcan.Gbg.rep0 <- neet2[which(neet2$Cannabis==1 & neet2$Gender!="all" & is.na(neet2$Repeated_sample)),]

head(MHcan.Gbg.rep0)
```



## DRUG 

drug = 1, gender = all, repeated sample = 0

```{r}
MHdrg.Gall.rep0 <- neet2[which(neet2$Drug==1 & neet2$Gender=="all" & is.na(neet2$Repeated_sample)),]

head(MHdrg.Gall.rep0)

meta.MHdrg.Gall.rep0 <- metagen(OR_ln,
                                SE,
                                data=MHdrg.Gall.rep0,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHdrg.Gall.rep0
```

### DRUG - directionality

```{r}
MHdrg.Gall.rep1 <- neet2[which(neet2$Drug==1 & neet2$Gender=="all"),]

head(MHdrg.Gall.rep1)

meta.MHdrg.Gall.rep1 <- metagen(OR_ln,
                                SE,
                                data=MHdrg.Gall.rep1,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHdrg.Gall.rep1

meta.MHdrg.Gall.rep1.dir<-update.meta(meta.MHdrg.Gall.rep1, 
                                      byvar=Temporality.of.measures, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHdrg.Gall.rep1.dir

forest(meta.MHdrg.Gall.rep1.dir)
```


### DRUG - geography

```{r}
meta.MHdrg.Gall.rep0.geo<-update.meta(meta.MHdrg.Gall.rep0, 
                                      byvar=Country, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHdrg.Gall.rep0.geo

forest(meta.MHdrg.Gall.rep0.geo)
```

### DRUG - gender

```{r}
MHdrg.Gbg.rep0 <- neet2[which(neet2$Drug==1 & neet2$Gender!="all" & is.na(neet2$Repeated_sample)),]

head(MHdrg.Gbg.rep0)

meta.MHdrg.Gbg.rep0 <- metagen(OR_ln,
                               SE,
                               data=MHdrg.Gbg.rep0,
                               studlab=paste(Study),
                               comb.fixed = FALSE,
                               comb.random = TRUE,
                               method.tau = "DL",
                               hakn = FALSE,
                               prediction=FALSE,
                               sm="OR")
meta.MHdrg.Gbg.rep0


meta.MHdrg.Gbg.rep0<-update.meta(meta.MHdrg.Gbg.rep0, 
                                 byvar=Gender, 
                                 comb.random = TRUE, 
                                 comb.fixed = FALSE)
meta.MHdrg.Gbg.rep0

forest(meta.MHdrg.Gbg.rep0)
```



## SUICIDAL

suicidal = 1, gender = all, repeated sample = 0

```{r}
MHsui.Gall.rep0 <- neet2[which(neet2$Suicidal==1 & neet2$Gender=="all" & is.na(neet2$Repeated_sample)),]

head(MHsui.Gall.rep0)

meta.MHsui.Gall.rep0 <- metagen(OR_ln,
                                SE,
                                data=MHsui.Gall.rep0,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHsui.Gall.rep0
```


### SUICIDAL - directionality

```{r}
MHsui.Gall.rep1 <- neet2[which(neet2$Suicidal==1 & neet2$Gender=="all"),]

head(MHsui.Gall.rep1)

meta.MHsui.Gall.rep1 <- metagen(OR_ln,
                                SE,
                                data=MHsui.Gall.rep1,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHsui.Gall.rep1

meta.MHsui.Gall.rep1.dir<-update.meta(meta.MHsui.Gall.rep1, 
                                      byvar=Temporality.of.measures, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHsui.Gall.rep1.dir

forest(meta.MHsui.Gall.rep1.dir)
```

### SUICIDAL - geography

```{r}
meta.MHsui.Gall.rep0.geo<-update.meta(meta.MHsui.Gall.rep0, 
                                      byvar=Country, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHsui.Gall.rep0.geo

forest(meta.MHsui.Gall.rep0.geo)
```


### SUICIDAL - gender

```{r}
MHsui.Gbg.rep0 <- neet2[which(neet2$Suicidal==1 & neet2$Gender!="all" & is.na(neet2$Repeated_sample)),]

head(MHsui.Gbg.rep0)
```


## ANY

any = 1, gender = all, repeated sample = 0

```{r}
MHany.Gall.rep0 <- neet2[which(neet2$Any==1 & neet2$Gender=="all" & is.na(neet2$Repeated_sample)),]

head(MHany.Gall.rep0)
```

Gen says to only use Power 2015's "Any lifetime disorder" here and "Any dx in adol" for directionality

```{r}
MHany.Gall.rep0 <- MHany.Gall.rep0[c(1,2,4),]

head(MHany.Gall.rep0)

meta.MHany.Gall.rep0 <- metagen(OR_ln,
                                SE,
                                data=MHany.Gall.rep0,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHany.Gall.rep0
```

### ANY - directionality

```{r}
MHany.Gall.rep0 <- neet2[which(neet2$Any==1 & neet2$Gender=="all" & is.na(neet2$Repeated_sample)),]

head(MHany.Gall.rep0)
```

Gen says to only use Power 2015's "Any dx in adol" for directionality
```{r}
MHany.Gall.rep0 <- MHany.Gall.rep0[c(1,3,4),]

head(MHany.Gall.rep0)

meta.MHany.Gall.rep0 <- metagen(OR_ln,
                                SE,
                                data=MHany.Gall.rep0,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHany.Gall.rep0


meta.MHany.Gall.rep0.dir<-update.meta(meta.MHany.Gall.rep0, 
                                      byvar=Temporality.of.measures, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHany.Gall.rep0.dir

forest(meta.MHany.Gall.rep0.dir)
```


### ANY - geography

In order to go back to "any lifetime disorder" for subgroup analysis by geography, must regenerate the original subset.

```{r}
MHany.Gall.rep0 <- neet2[which(neet2$Any==1 & neet2$Gender=="all" & is.na(neet2$Repeated_sample)),]

head(MHany.Gall.rep0)
```


going back to "any lifetime disorder" only

```{r}
MHany.Gall.rep0 <- MHany.Gall.rep0[c(1,2,4),]

head(MHany.Gall.rep0)

meta.MHany.Gall.rep0 <- metagen(OR_ln,
                                SE,
                                data=MHany.Gall.rep0,
                                studlab=paste(Study),
                                comb.fixed = FALSE,
                                comb.random = TRUE,
                                method.tau = "DL",
                                hakn = FALSE,
                                prediction=FALSE,
                                sm="OR")
meta.MHany.Gall.rep0

meta.MHany.Gall.rep0.geo<-update.meta(meta.MHany.Gall.rep0, 
                                      byvar=Country, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta.MHany.Gall.rep0.geo

forest(meta.MHany.Gall.rep0.geo)
```


### ANY - gender

```{r}
MHany.Gbg.rep0 <- neet2[which(neet2$Any==1 & neet2$Gender!="all" & is.na(neet2$Repeated_sample)),]

head(MHany.Gbg.rep0)
```

